Sentence Generation as Planning with Probabilistic LTAG\\

### 2010-05-21 trunk/Papers/pcrisp-10/pcrisp-10.tex
done.

\author{Daniel Bauer\\
  Department of Computer Science\\
  Columbia University\\
  1214 Amsterdam Ave.\\
  New York, NY 10027, USA\\
  {\tt bauer@cs.columbia.edu} 
  \And
  Alexander Koller\\
  Cluster of Excellence\\ ``Multimodal Computing and Interaction''\\
  Saarland University\\
  66041 Saarbr\"{u}cken, Germany\\ 
  {\tt koller@mmci.uni-saarland.de}}

>>>>

\author{Daniel Bauer\\
  Department of Computer Science\\
  Columbia University\\
  1214 Amsterdam Ave.\\
  New York, NY 10027, USA\\
  {\tt bauer@cs.columbia.edu} 
  \And
  Alexander Koller\\
  Cluster of Excellence\\
  Saarland University\\
  Campus C7 4\\
  66041 Saarbr\"{u}cken, Germany\\ 
  {\tt koller@mmci.uni-saarland.de}}
